Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2017-12-06 workflow/workflow.Rmd
change file name of dataObj after zinbwave
respond to Fanny comments

```{r}
# Filtering to top 1,000 most variable genes
vars <- rowVars(log1p(assay(dataObj)))
names(vars) <- rownames(dataObj)
vars <- sort(vars, decreasing = TRUE)
dataObj <- dataObj[names(vars)[1:1000],]
```

EP: If use SingleCellFilter (or davide adds to singleCellExperiment) could do this in 1 line.

EP: Why do we create 'core' rather than just replace 'dataObj'.   
FP: I agree, I think that it is unnecessary. I changed 'core' to dataObj.

@@

```{r}
#save(dataObj, file= 'dataObj.rda')
load('dataObj.rda')
```

@@

@@

EP: If zinbwave already has been updated, this above code is probably not needed since its aready there.  
FP: As the name/type "zinbwave50" is then needed in the RSEC function, we might need to keep this line.

@@

plotHeatmap(dataObj, 
            whichClusters = "primary", clusterFeaturesData = "all",
            clusterSamplesData = "dendrogramValue", breaks = 0.99,
            sampleData = c("Batch", "Experiment"),
            clusterLegend = metaColors, annLegend = FALSE, main = "")
```

@@

FP: publishedClusters does not appear in the bars.

@@

```{r mdsWce, fig.cap="RSEC: MDS of the low-dimensional matrix W, where each point represents a cell and cells are color-coded by RSEC clustering."}
plotDimReduce(dataObj,whichCluster="primary",reduceMethod="zinbwave50",pch=20,
	xlab = "Component1", ylab = "Component2",legendTitle="Sample",main=""
)
```
FP: I get `"reduceMethod" is not a graphical parameter`. I think this plot is different from the previous version.

@@

FP: this plot is fairly different from the previous version. We should see for one cluster that the gene expression for Reg3g is much high that for the other clusters.

EP: not sure why needed 'c4' object. This is new function. Tell me if you run into problems.

>>>>

```{r}
# # Filtering to top 1,000 most variable genes
# vars <- rowVars(log1p(assay(dataObj)))
# names(vars) <- rownames(dataObj)
# vars <- sort(vars, decreasing = TRUE)
# dataObj <- dataObj[names(vars)[1:1000],]

#alternative script:
dataObj<-makeFilterStats(dataObj,filterStats="var")
dataObj<-filterData(dataObj,percentile=1000)
```

EP: Added existing code in the clusterExperiment package that does this. Also will mean that any future steps in package that need variance for the dataObj will have variance per gene stored.

@@

```{r}
#save(dataObj, file= 'dataObj_afterZinbwave.rda')
load('dataObj_afterZinbwave.rda')
```

@@

EP: I would get rid of the `SingleCellExperiment::` code and just add a `library(SingleCellExperiment)`. Much more comfortable code for most users.

@@

EP: If zinbwave already has been updated, this above code is probably not needed since its aready there.  
FP: As the name/type "zinbwave50" is then needed in the RSEC function, we might need to keep this line.
EP: I just called it "zinbwave50". We can replace that with whatever its name is in the results from zinbwave. It needs a name, but it can be anything.

@@

plotHeatmap(dataObj, 
            whichClusters = c("primary","PublishedClusters"), clusterFeaturesData = "all",
            clusterSamplesData = "dendrogramValue", breaks = 0.99,
            sampleData = c("Batch", "Experiment"),
            clusterLegend = metaColors, annLegend = FALSE, main = "")
```

@@

FP: publishedClusters does not appear in the bars.
EP: I forgot to add it to the `whichClusters` argument.

@@

```{r mdsWce, fig.cap="RSEC: MDS of the low-dimensional matrix W, where each point represents a cell and cells are color-coded by RSEC clustering."}
plotDimReduce(dataObj,whichCluster="primary",reducedDim="zinbwave50",pch=20,
	xlab = "Component1", ylab = "Component2",legendTitle="Sample",main=""
)
```
FP: I get `"reduceMethod" is not a graphical parameter`. I think this plot is different from the previous version.
EP: I had wrong name for argument (should have been `reducedDim`), so it went with default which is PCA on the assay(dataObj) slot -- i.e. not using zinbwave. Hopefully better now.

@@

FP: this plot is fairly different from the previous version. We should see for one cluster that the gene expression for Reg3g is much high that for the other clusters.  
EP: I think this plot is of the normalized values (saved in assay(dataObj)). But I see that the previous plot was on the counts. Is that better than normalized value?
